Large-scale harmonic patterns clustering

### 2010-03-21 Paper/Paper.tex
improved
improved by tbm

Note that we do not claim that any of these informations (segments, beats, bars)
are perfectly accurate (e.g. in \cite{Barrington2009a} authors obtain a better
song segmentation than Echonest). Practise showed us that they are reasonable, 
and the size of the data set should make up for the imperfections or noise.
We also believe that patches sizes based on a number of beats or bars are more
meaningful than an arbitrary time length. More on this in the experiments
(Section \ref{sec:experiments}).

@@

\section{Experiments - Fundamentals}\label{sec:experiments}
Note that we will present two additional experiments in 
Section \ref{sec:exps2}.

@@

% NEW RESULTS COMING SOON WITH FIXED SIZED DATASET
\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.066079$ \\
10 & $5$K & $0.045690$ \\
50 & $25$K & $0.038456$ \\
100 & $50$K & $0.036725$ \\
200 & $100$K & $0.033923$ \\
500 & $250$K & $0.030973$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{\small{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. The number of training
samples is set to $500$ times the number of codes, which is sufficient
according to Figure \ref{fig:sizes}. NEW RESULTS COMING SOON WITH FIXED 
SIZED DATASET }}
\label{tab:cbsize}
\end{table}

@@

\subsection{Music Randomness}
It will not surprise any reader, music is not random. This fact should
become apparent in our experiments in the following way. Information
theory tells us that if the signal to encode doubles, we need to square
the size of the codebook to encode it with the same distortion.

@@

Since music is not random, we expect that squaring the codebook when the
pattern size doubles will rather give improved results than constant ones.
See Figure \ref{it's comng...}.

>>>>

Note that we do not claim that any of these informations (segments, beats, bars)
are perfectly accurate (e.g. in \cite{Barrington2009a} authors obtain a better
song segmentation than Echonest). Practise showed us that they are reasonable, 
and the size of the data set should make up for the imperfections or noise.
We also believe that patches sizes based on a number of beats or bars are more
meaningful than an arbitrary time length. More on this in the experiments
(Section \ref{sec:experiments} TO BE CHECKED).

@@

\section{Experiments - Fundamentals}\label{sec:experiments}
In this section we assert the basic properties of our encoding scheme.
The first subsection gives the details to reproduce the experiments,
such as the distance measure and learning rate. In second subsection, we
measure properties such as ``how the number of codes affect the distortion''
and ``how many learning samples should we use''. Though important numbers
to report, the busy reader could skip to subsection \ref{ssec:random}
and the following sections.
Note that we will present two additional experiments in 
Section \ref{sec:exps2}.

@@

% NEW RESULTS COMING SOON WITH FIXED SIZED DATASET
\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.066079$ \\
10 & $5$K & $0.045690$ \\
50 & $25$K & $0.038456$ \\
100 & $50$K & $0.036725$ \\
200 & $100$K & $0.033923$ \\
500 & $250$K & $0.030973$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{\small{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. The number of training
samples is set to $500$ times the number of codes. 
NEW RESULTS COMING SOON WITH FIXED SIZED DATASET }}
\label{tab:cbsize}
\end{table}

@@

\subsection{Music Randomness}\label{ssec:random}
It will not surprise any reader, music is not random. This fact should
become apparent in our experiments in the following way. Information
theory tells us that if the signal to encode doubles, we need to square
the size of the codebook to encode it with the same distortion.

@@

Since music is not random, we expect that squaring the codebook when the
pattern size doubles will rather give improved results than constant ones.
See Figure \ref{fig:size_pattern}.

% see generate_expo_codes_curves.py to generate the following figure:
\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{codesize_patternsize}
\end{center}
\caption{\small{NEW RESULTS COMING IN}}
\label{fig:size_pattern}
\end{figure}
